\documentclass{lea}

%%
%% Setup
%%

\title{ENIGMA HALFpipe: Interactive, reproducible, and efficient analysis for resting-state and task-based fMRI data}

\author[1\envelope]{Lea Waller \orcid{0000-0002-3239-6957}}
\author[1]{Susanne Erk}
\author[2,3]{Elena Pozzi \orcid{0000-0001-8360-5571}}
\author[2,3]{Yara J. Toenders \orcid{0000-0002-4117-1143}}
\author[4]{Courtney~C.~Haswell}
\author[1]{Marc Büttner \orcid{0000-0001-6940-6656}}
\author[5]{Paul M. Thompson \orcid{0000-0002-4720-8867}}
\author[2,3]{Lianne Schmaal \orcid{0000-0001-9822-048X}}
\author[4]{Rajendra~A.~Morey \orcid{0000-0002-6517-6969}}
\author[1]{Henrik Walter \orcid{0000-0002-9403-6121}}
\author[1,6]{Ilya M. Veer \orcid{0000-0002-6733-3593}}

\affil[1]{Department of Psychiatry and Psychotherapy CCM, Charité Universitätsmedizin Berlin, corporate member of Freie Universität Berlin and Humboldt-Universität zu Berlin, Berlin, Germany}
\affil[2]{Centre for Youth Mental Health, University of Melbourne, Melbourne, Australia}
\affil[3]{Orygen, Parkville, Australia}
\affil[4]{Duke University School of Medicine, Durham, NC, USA}
\affil[5]{Imaging Genetics Center, Mark and Mary Stevens Institute for Neuroimaging and Informatics, Keck School of Medicine, University of Southern California, Los Angeles, CA, USA}
\affil[6]{Donders Institute for Brain, Cognition and Behaviour, Nijmegen, the Netherlands; Radboud University Medical Center, Nijmegen, the Netherlands}
\affil[\envelope]{Correspondence should be addressed to \href{mailto://lea@fmri.science}{lea@fmri.science}}

\fancyhead[L]{\sffamily Waller et al.}
\fancyhead[R]{\sffamily ENIGMA HALFpipe | {\fontseries{mb}\selectfont\color{leaPurple}\thepage}}

\fancyfoot[C]{}
%\fancyfoot[R]{\sffamily%
%\href{https://github.com/HALFpipe/HALFpipe}{\color{leaPurple}{https://github.com/HALFpipe/HALFpipe}}}

%%
%% Article
%%

\begin{document}

\maketitle

\begin{abstract}

The reproducibility crisis in neuroimaging has led to an increased
demand for standardized data processing workflows. Within the ENIGMA
consortium, we developed \soft{HALFpipe} (\soft{H}armonized 
\soft{A}na\soft{L}ysis of \soft{F}unctional MRI 
\soft{pipe}line), an open-source, containerized, user-friendly tool that
facilitates reproducible analysis of task-based and resting-state fMRI
data through uniform application of preprocessing, quality assessment,
single-subject feature extraction, and group-level statistics. It
provides state-of-the-art preprocessing using \soft{fMRIPrep} without the
requirement for input data in Brain Imaging Data Structure (BIDS)
format. \soft{HALFpipe} extends the functionality of \soft{fMRIPrep} with additional
preprocessing steps, which include spatial smoothing, grand mean
scaling, temporal filtering, and confound regression. \soft{HALFpipe} generates
an interactive quality assessment (QA) webpage to assess the quality of
key preprocessing outputs and raw data in general. \soft{HALFpipe} features
myriad post-processing functions at the individual subject level,
including calculation of task-based activation, seed-based connectivity,
network-template (or dual) regression, atlas-based functional
connectivity matrices, regional homogeneity (ReHo), and fractional
amplitude of low frequency fluctuations (fALFF), offering support to
evaluate a combinatorial number of features or preprocessing settings in
one run. Finally, flexible factorial models can be defined for
mixed-effects regression analysis at the group level, including multiple
comparison correction. Here, we introduce the theoretical framework in
which \soft{HALFpipe} was developed, and present an overview of the main
functions of the pipeline. \soft{HALFpipe} offers the scientific community a
major advance toward addressing the reproducibility crisis in
neuroimaging, providing a workflow that encompasses preprocessing,
post-processing, and QA of fMRI data, while broadening core principles
of data analysis for producing reproducible results. Instructions and 
code can be found at \url{https://github.com/HALFpipe/HALFpipe}.

\end{abstract}

\input{./tex/introduction.tex}

\input{./tex/methods.tex}

\input{./tex/procedure.tex}

\input{./tex/discussion.tex}

\section{Acknowledgements}

S.E. acknowledges funding from the German Research Foundation (DFG ER
724/4--1).
P.M.T. received research grant funding from Biogen, Inc., for research unrelated to this manuscript.
L.S. acknowledges funding from the National Institutes of Health (NIH RO1
MH117601 and NHMRC Career Development Fellowship 1140764).
R.A.M acknowledges funding from National Institutes of Health (NIH R01
MH111671).
H.W. acknowledges funding from the German Research Foundation (DFG WA
1539/11--1).
I.V. acknowledges funding from the European Union's Horizon 2020 research
and innovation programme under under Grant Agreement number 777084
(DynaMORE project).

\bibliography{./bib/lea,./bib/ilya}

\end{document}
